---
title: "simplin"
output: rmarkdown::html_vignette
author: "Hanxiao Jing"
vignette: >
  %\VignetteIndexEntry{simplin}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(simplin)
```

## Introduction

Here are an example on how to fit simple linear regression models using this package.

## Model

Consider simple linear regression model 
$$Y_i=\beta_0+\beta_1X_i+\epsilon_i\quad i=1,2,\dots,n$$ 
Suppose we observe $X_1,X_2,\dots,X_n$ and $Y_1,Y_2,\dots,Y_n$, and want to estimate $\beta_0$ and $\beta_1$.

## Input and Output

To fit a simple linear regression model, use function `simp_lin_R`
```{r}
x <- 1:10
y <- 2+1.5*x+rnorm(10)
fit1 <- simp_lin_R(x,y)
```
where `x` and `y` should be numeric vectors.

The output is a list containing coefficients (`coef`), predictions (`pred`) and residuals (`res`).
```{r}
fit1
```
where `coef` is a matrix containing the estimated values, standard errors and 95% confidence intervals for $\hat{\beta_0}$ and $\hat{\beta_1}$.
